---
title: "Final_extensions2"
author: "Simon Jean"
date: "2024-07-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

rm(list = ls())
library(magrittr)
library(dplyr)
library(reshape2)
library(ggplot2)
library(landscapeR)
library(raster)
library(NLMR)
library(Matrix)
library(combinat)
library(here)
library(parallel)
```

## Work with 1 landscape
```{r, declare size}
size = 100

```


```{r, own}
#fictitious_landscape = matrix(round(runif(size^2,0,2 )), nrow = size, ncol = size)

#viz_landscape(landscapes[1])

#viz_landscape1 = matrix(landscapes[1], size, size)
#viz_landscape(viz_landscape1)

#treatment = matrix(round(runif(size^2, 0, 1)), nrow = size, ncol = size)

#viz_landscape(matrix(next_landscape(fictitious_landscape, treatment),100,100))


m  = matrix(0, size, size)
r  = raster(m, xmn = 0, xmx = size, ymn = 0, ymx = size)

num1 = round(runif(1, 0, 2*size))
size1 = round(runif(num1, 1, .8*size))
rr = makeClass(r, num1, size1, val= 1)

num2 = round(runif(1, 0, 2*size))
if(num2 == 0){
  size2 == 0
}else{
  size2 = round(runif(num2, 1, .8*size))
}
rr = makeClass(rr, num2, size2, val = 2)
plot(rr)

```

Now several questions emerge : 

1. How do we evaluate the landscape with respect to our metrics : need a huge adjacency matrix.

```{r, adjacency matrix}
kings_graph  =  function(n, timer_ = T) {
  if(timer_ == T){
    start = Sys.time()
  }
  # Initialize the adjacency matrix with zeros
  adj_matrix  =  Matrix(0, nrow = n*n, ncol = n*n, sparse = T)
  # Define potential moves (king moves in chess)
  moves  =  rbind(c(-1, -1), c(-1, 0), c(-1, 1), c(0, -1), c(0, 1), c(1, -1), c(1, 0), c(1, 1), c(0,0))

  # Helper function to safely add edges
  add_edge  =  function(i, j) {
    if (i >= 1 && i <= n*n && j >= 1 && j <= n*n) {
      adj_matrix[i,j]  =  1
      adj_matrix[j,i]  =  1
    }
    return(adj_matrix)
  }
  
  # Map each square to its neighbors
  for (row in 1:n) {
    for (col in 1:n) {
      index  =  (row - 1) * n + col
      
      for (move in 1:nrow(moves)) {
        neighbor_row  =  row + moves[move, 1]
        neighbor_col  =  col + moves[move, 2]
        if (neighbor_row > 0 && neighbor_row <= n && neighbor_col > 0 && neighbor_col <= n) {
          neighbor_index  =  (neighbor_row - 1) * n + neighbor_col
          if(adj_matrix[index,neighbor_index] == 0){
            adj_matrix = add_edge(index, neighbor_index) 
          }
        }
      }
    }
  }
  if(timer_ == T){
    end  =  Sys.time()
    time_taken  =  end - start
    return(list(matrix = adj_matrix, time = time_taken))
  } else {
    return(adj_matrix)
  }
}

test__ = F
if(test__ == T){
  adjacency_ = matrix(nrow = 9, ncol = 9)
adjacency_[1, ] = c(1, 1, 0, 1, 1, 0, 0, 0, 0)
adjacency_[2, ] = c(1, 1, 1, 1, 1, 1, 0, 0, 0)
adjacency_[3, ] = c(0, 1, 1, 0, 1, 1, 0, 0, 0)
adjacency_[4, ] = c(1, 1, 0, 1, 1, 0, 1, 1, 0)
adjacency_[5, ] = c(1, 1, 1, 1, 1, 1, 1, 1, 1)
adjacency_[6, ] = c(0, 1, 1, 0, 1, 1, 0, 1, 1)
adjacency_[7, ] = c(0, 0, 0, 1, 1, 0, 1, 1, 0)
adjacency_[8, ] = c(0, 0, 0, 1, 1, 1, 1, 1, 1)
adjacency_[9, ] = c(0, 0, 0, 0, 1, 1, 0, 1, 1)

adjacency_ == kings_graph(3)$matrix
}


# package sparse, Matrix, Big Memory
adjacency_ = kings_graph(size)$matrix
#teswrite.csv(test, 'king_adjacency_50.csv')
```

May be able to generate neutral landscape models with `NLMPy`, in Python, or check `NLMR`and `landscapetools` in R, although they disappeared from CRAN.

```{r, compute the scores}
mature_cells = function(matrix){
  to_ret = Matrix(as.numeric(matrix<2), ncol = 1, sparse = T)
  return(to_ret)
}

burn_cells = function(matrix){
  to_ret = Matrix(as.numeric(matrix>1), ncol = 1, sparse = T)
  return(to_ret)
}

mature_score = function(matrix, 
                        type_ = 'B',
                        adj_ = adjacency_){
  if(type_ == 'B'){
    return(t(mature_cells(matrix)) %*% adj_ %*% mature_cells(matrix))
  }else{
    return(t(burn_cells(matrix)) %*% adj_ %*% burn_cells(matrix))
  }
}


mature_score(rr@data@values, type_ = "F")
mature_score(rr@data@values, type_ = 'B')


plot(rr)

```
```{r, dynamics}

age_dyn = function(landscape, treatment){
  landscape = Matrix(landscape, ncol = 1, sparse = T)
  treatment = Matrix(treatment, ncol = 1, sparse = T)
  
  augmented_mat = landscape + 1
  capped_mat = pmin(augmented_mat, 2)
  treatment_ = 1 - treatment
  next_ = capped_mat * treatment_
  next_ = Matrix(as.numeric(next_), ncol = size, byrow= T, sparse = T)
  return(next_)
}

a = age_dyn(rr@data@values, round(runif(size^2)))

b = rr
values(b) = as.vector(a)
plot(b)
```
Now need to think of the dynamic programming approach:

1. Is the problem dynamic or can it be built as the sum of myopic approaches
2. Revisit the code to see how I did the dynamic optimization
  * Just did a bunch of myopic optimizations
  * Is it really dynamic? Can it be that the forest structure we look at makes it ok to have myopic solutions?
  * My existing solution is in fact dynamic, as I find the min for all existing landscapes. Therefore, it has to be a succession of mins.
  * Why would it be different here? Could I do it over like 5 periods?
3. To do next : 
  * Do the optimization procedure for 5 periods on size 4 landscapes for a given budget
  
  
```{r, generate all possible landscapes}
values = c(0,1,2)

equi_landscape = function(land){
  # 3 transformations clockwise rotation
  m2  =  t(apply(land, 2, rev))
  m3  =  t(apply(m2, 2, rev))
  m4  =  t(apply(m3, 2, rev))
  
  # Horizontal symmetry
  hor_sym  =  land[nrow(land):1, ]
  
  # 3 clockwise transformations of horizontally symmetrized matrix
  m6  =  t(apply(hor_sym, 2, rev))
  m7  =  t(apply(m6, 2, rev))
  m8  =  t(apply(m7, 2, rev))
  
  # Combine all equivalent matrices into a list
  equivalences  =  list(as.vector(m2), as.vector(m3), as.vector(m4), as.vector(hor_sym), as.vector(m6), as.vector(m7), as.vector(m8))
  
  return(unique(equivalences))
}

generate_vectors_with_twos <- function(N, x, y) {
  # Initialize an empty list to store the result vectors
  result_vectors <- list()
  
  # Special case: if there are no ones or no twos
  if (y == 0) {
    combinations_ones <- combn(N, x)
    for (i in 1:ncol(combinations_ones)) {
      vector <- rep(0, N)
      vector[combinations_ones[, i]] <- 1
      result_vectors[[length(result_vectors) + 1]] <- vector
    }
    return(result_vectors)
  }
  
  if (x - y == 0) {
    combinations_twos <- combn(N, y)
    for (i in 1:ncol(combinations_twos)) {
      vector <- rep(0, N)
      vector[combinations_twos[, i]] <- 2
      result_vectors[[length(result_vectors) + 1]] <- vector
    }
    return(result_vectors)
  }
  
  # General case: generate all combinations of positions for the 1s
  combinations_ones <- combn(N, x)
  
  # Iterate over each combination of positions for 1s
  for (i in 1:ncol(combinations_ones)) {
    # Create a base vector of zeros
    base_vector <- rep(0, N)
    
    # Place 1s in the specified positions
    base_vector[combinations_ones[, i]] <- 1
    
    # Generate all combinations of positions within the selected 1s to change to 2s
    positions_ones <- combinations_ones[, i]
    combinations_twos <- combn(positions_ones, y)
    
    # Iterate over each combination of positions for 2s
    for (j in 1:ncol(combinations_twos)) {
      # Create a copy of the base vector
      vector <- base_vector
      
      # Place 2s in the specified positions
      vector[combinations_twos[, j]] <- 2
      
      # Add the vector to the result list
      result_vectors[[length(result_vectors) + 1]] <- vector
    }
  }
  
  return(result_vectors)
}

landscape_to_hash <- function(landscape) {
  return(paste(as.vector(landscape), collapse = ","))
}

low_lev_land4 = function(nb_nonz, nb2, size. = size) {
  #
  potential_landscapes = generate_vectors_with_twos(size.^2, nb_nonz, nb2)
  unique_landscapes = list()
  seen_hashes =  character(0)
  
  for (landscape in potential_landscapes) {
    matrix_landscape = matrix(landscape, nrow = size.)
    equiv_landscapes = equi_landscape(matrix_landscape)
    
    is_unique <- TRUE
    for (equiv in equiv_landscapes) {
      hash_equiv = landscape_to_hash(equiv)
      if (hash_equiv %in% seen_hashes) {
        is_unique <- FALSE
        break
      }
    }
    
    if (is_unique) {
      unique_landscapes[[length(unique_landscapes) + 1]] <- landscape
      for (equiv in equiv_landscapes) {
        seen_hashes <- c(seen_hashes, landscape_to_hash(equiv))
      }
    }
  }
  unique_landscapes = Matrix(do.call(rbind, unique_landscapes), sparse = T)
  return(unique_landscapes)
}

# Generate landscapes
all_objects = ls(envir = .GlobalEnv)
all_functions = all_objects[sapply(all_objects, function(x) is.function(get(x)))]

numCores = 8

for(nb_nonz_ in 1:6){
  start = Sys.time()
  
  nb2_ = seq(0,nb_nonz_)
  candidates_ = mapply(list, rep(nb_nonz_, nb_nonz_+1), nb2_, SIMPLIFY = F)
  
  cl = makeCluster(numCores)
  clusterExport(cl, varlist = c(all_functions, 'nb2_', 'nb_nonz_', "size"))
  clusterEvalQ(cl,{
    library(Matrix)
    library(combinat)
  })
  
  result = parLapply(cl, candidates_, function(inputs){
    low_lev_land4(inputs[[1]], inputs[[2]])
  })
  
  for(i in 1:length(result)){
    writeMM(result[i][[1]], file = here('landscapes_4x4', paste0("landscapes4_", candidates_[i][[1]][[1]],'_', candidates_[i][[1]][[2]],'.mtx')))
  }
  
  #for(nb2_ in 0:nb_nonz_){
  #  dat_ = low_lev_land4(nb_nonz_, nb2_)
  #  writeMM(dat_, file = here('landscapes_4x4', paste0("landscapes4_", nb_nonz_, '_', nb2_,'.mtx')))
  #}
  print(paste('Step', nb_nonz_, 'took', round(Sys.time() - start,3)))
}


```



  
```{r, generate treatments for a given budget}
budget = 3
number_treats   = paste0('choose(', size^2 ,',', seq(1:budget),')' )
number_treats   = eval(parse(text= paste(number_treats, collapse = '+')))
potential_treat = vector('list', number_treats)


generate_combinations  =  function(N, k_max) {
  all_combinations  =  list()
  total_columns  =  0
  
  for (k in 1:k_max) {
    comb  =  combn(N, k)
    total_columns  =  total_columns + ncol(comb)
    binary_vectors  =  apply(comb, 2, function(indices) {
      vec  =  rep(0, N)
      vec[indices]  =  1
      return(vec)
    })
    all_combinations[[k]]  =  binary_vectors
  }
  
  # Combine all combinations into a single matrix
  combined_matrix  =  do.call(cbind, all_combinations)
  
  # Convert to sparse matrix
  sparse_comb_matrix  =  Matrix(combined_matrix, sparse = TRUE)
  
  return(sparse_comb_matrix)
}

treat = generate_combinations(size^2, round(size^2/5))
```


What would dynamic programming look like here? Under what conditions is the fact that the problem is broken in different little pieces ok? 
What is said to be dynamic programming is not in our approach : it is not enough to find the minimum of given successions, otherwise it is just a static problem. 

```{r, value function iteration}

to_optimize = function(landscape, treatment, constraint_){
  y = mature_score(landscape, type_='F') + ifelse(mature_score(landscape) <= constraint_, 10^5, 0)
}

# Steps following Chris : 
# 1. Set all parameters : 
Time_horizon = 20
# 2. Discretize the state space into N equally spaced values for the control
head(treat)
# 3. Set possible value functions over T+1 periods, with T+1 = 0
value_functions_ = vector('list', Time_horizon + 1)
value_functions_[Time_horizon + 1] = 



```