---
title: "Final extension"
author: "Simon Jean"
date: "2024-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

rm(list = ls())
library(magrittr)
library(dplyr)
library(reshape2)
library(ggplot2)
library(landscapeR)
library(raster)
library(NLMR)
library(Matrix)
```

## Analysis of real looking landscapes in light of our results
Set landscape size : 

```{r, parameter and functions}
size = 100

viz_landscape = function(landscape){
 melt(landscape)%>%
    mutate(value = as.factor(value))%>%
    ggplot(aes(x= Var1, y = Var2, fill = value))+
    geom_tile()+
    scale_fill_manual(values= c('white', 'orange', 'red'))+
    theme_minimal()
}

next_landscape = function(landscape, treatment){
  vector_version = c(landscape)
  next_landscape = pmin((1+vector_version), rep(2,length(vector_version)))
  next_landscape = next_landscape * (1 - c(treatment))
  return(next_landscape)
}

```

Now originate landscape : 

```{r, }
landscapes = list()
nlandscape = 15
for(x in 1:nlandscape){
    m  = matrix(0, size, size)
    r  = raster(m, xmn = 0, xmx = size, ymn = 0, ymx = size)
    num1 = round(runif(1, 0, size))
    size1 = round(runif(num1, 1, .8*size))
    rr = makeClass(r, num1, size1, val= 1)

    num2 = round(runif(1, 0, size))
    size2 = round(runif(num2, 1, .8*size))
    rr = makeClass(rr, num2, size2, val = 2)
    plot(rr)
    landscapes = append(landscapes, list(rr@data@values))
}


```

Now this teaches several things : 

1. First, better to work with raster format

2. It may make sense to store the rasters in a nested list to have the intertemporal profile of management compared to initial conditions

3. It is still unclear how we test our hypothesis and generate the treatment though

## Work with 1 landscape

```{r, own}
#fictitious_landscape = matrix(round(runif(size^2,0,2 )), nrow = size, ncol = size)

#viz_landscape(landscapes[1])

#viz_landscape1 = matrix(landscapes[1], size, size)
#viz_landscape(viz_landscape1)

#treatment = matrix(round(runif(size^2, 0, 1)), nrow = size, ncol = size)

#viz_landscape(matrix(next_landscape(fictitious_landscape, treatment),100,100))

size = 80

m  = matrix(0, size, size)
r  = raster(m, xmn = 0, xmx = size, ymn = 0, ymx = size)

num1 = round(runif(1, 0, size))
size1 = round(runif(num1, 1, .8*size))
rr = makeClass(r, num1, size1, val= 1)

num2 = round(runif(1, 0, size))
if(num2 == 0){
  size2 == 0
}else{
  size2 = round(runif(num2, 1, .8*size))
}
rr = makeClass(rr, num2, size2, val = 2)
plot(rr)

```

Now several questions emerge : 

1. How do we evaluate the landscape with respect to our metrics : need a huge adjacency matrix.

```{r, adjacency matrix}
kings_graph <- function(n, timer_ = T) {
  if(timer_ == T){
    start = Sys.time()
  }
  # Initialize the adjacency matrix with zeros
  adj_matrix <- Matrix(0, nrow = n*n, ncol = n*n)
  # Define potential moves (king moves in chess)
  moves <- rbind(c(-1, -1), c(-1, 0), c(-1, 1), c(0, -1), c(0, 1), c(1, -1), c(1, 0), c(1, 1), c(0,0))

  # Helper function to safely add edges
  add_edge <- function(i, j) {
    if (i >= 1 && i <= n*n && j >= 1 && j <= n*n) {
      adj_matrix[i,j] <- 1
      adj_matrix[j,i] <- 1
    }
    return(adj_matrix)
  }
  
  # Map each square to its neighbors
  for (row in 1:n) {
    for (col in 1:n) {
      index <- (row - 1) * n + col
      
      for (move in 1:nrow(moves)) {
        neighbor_row <- row + moves[move, 1]
        neighbor_col <- col + moves[move, 2]
        if (neighbor_row > 0 && neighbor_row <= n && neighbor_col > 0 && neighbor_col <= n) {
          neighbor_index <- (neighbor_row - 1) * n + neighbor_col
          if(adj_matrix[index,neighbor_index] == 0){
            adj_matrix = add_edge(index, neighbor_index) 
          }
        }
      }
    }
  }
  if(timer_ == T){
    end <- Sys.time()
    time_taken <- end - start
    return(list(matrix = adj_matrix, time = time_taken))
  } else {
    return(adj_matrix)
  }
}

test__ = F
if(test__ == T){
  adjacency_ = matrix(nrow = 9, ncol = 9)
adjacency_[1, ] = c(1, 1, 0, 1, 1, 0, 0, 0, 0)
adjacency_[2, ] = c(1, 1, 1, 1, 1, 1, 0, 0, 0)
adjacency_[3, ] = c(0, 1, 1, 0, 1, 1, 0, 0, 0)
adjacency_[4, ] = c(1, 1, 0, 1, 1, 0, 1, 1, 0)
adjacency_[5, ] = c(1, 1, 1, 1, 1, 1, 1, 1, 1)
adjacency_[6, ] = c(0, 1, 1, 0, 1, 1, 0, 1, 1)
adjacency_[7, ] = c(0, 0, 0, 1, 1, 0, 1, 1, 0)
adjacency_[8, ] = c(0, 0, 0, 1, 1, 1, 1, 1, 1)
adjacency_[9, ] = c(0, 0, 0, 0, 1, 1, 0, 1, 1)

adjacency_ == kings_graph(3)$matrix
}


# package sparse, Matrix, Big Memory
adjacency_ = kings_graph(size)$matrix
#teswrite.csv(test, 'king_adjacency_50.csv')
```

May be able to generate neutral landscape models with `NLMPy`, in Python, or check `NLMR`and `landscapetools` in R, although they disappeared from CRAN.

```{r, compute the scores}
mature_cells = function(matrix){
  to_ret = Matrix(as.numeric(matrix<2), ncol = 1, sparse = T)
  return(to_ret)
}

burn_cells = function(matrix){
  to_ret = Matrix(as.numeric(matrix>1), ncol = 1, sparse = T)
  return(to_ret)
}

mature_score = function(matrix, 
                        type_ = 'B',
                        adj_ = adjacency_){
  if(type_ == 'B'){
    return(t(mature_cells(matrix)) %*% adj_ %*% mature_cells(matrix))
  }else{
    return(t(burn_cells(matrix)) %*% adj_ %*% burn_cells(matrix))
  }
}


mature_score(rr@data@values, type_ = "F")
mature_score(rr@data@values, type_ = 'B')


plot(rr)

```



