---
title: "Attempt at optimization heurstics"
author: "Simon Jean"
date: "2024-07-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(dplyr)
library(ggplot2)
library(magrittr)
library(GA)
library(landscapeR)
library(here)
library(raster)
```


# I. Initiate landscape and visualization

In this setting, it would be interesting to be able to generate landscapes that have spatial autocorrelation. 

```{r, code_chunk}
# I. Parameters

size = 4
budget = round(size^2/5) +1
green_palette = c('0' = 'cornsilk',
                  '1' = 'lightgreen',
                  '2' = 'darkgreen')

# II. Generate landscape ####
m  = matrix(0, size, size)
r  = raster(m, xmn = 0, xmx = size, ymn = 0, ymx = size)

num1 = round(runif(1, 1, 2*size))
if(num1 == 0){
  size1 = 0
}else{
  size1 = round(runif(num1, 1, .8*size))
}
r = makeClass(r, num1, size1, val = 1)

num2 = round(runif(1, size*0.5, 2*size))
size2 = round(runif(num2, 1, .8*size))
rr = makeClass(r, num2, size2, val= 2)


# Visualization function 

viz_landscape = function(land){
  # Input is a raster
  as.data.frame(land, xy=T)%>%
  mutate(layer = as.factor(layer))%>%
  ggplot(aes(x=x,
             y=y,
             fill = layer))+
  geom_tile()+
  scale_fill_manual(values = green_palette)+
  theme_bw()
}

viz_landscape(rr)

```


Second, I convert the data to a `SparseMatrix`, and set up the `kings_graph()` function to generate adjacency matrices, as well as the payoff function to be optimized, including penalties for the biodiversity constraint and the budget constraints. 

```{r, convert raster to sparse and set up functions}
# Set landscape 
landscape = Matrix(rr@data@values, sparse = T)

#landscape = Matrix(2, nrow = size, ncol= size)

# Set adjacency
kings_graph  =  function(n, timer_ = T) {
  if(timer_ == T){
    start = Sys.time()
  }
  # Initialize the adjacency matrix with zeros
  adj_matrix  =  Matrix(0, nrow = n*n, ncol = n*n, sparse = T)
  # Define potential moves (king moves in chess)
  moves  =  rbind(c(-1, -1), c(-1, 0), c(-1, 1), c(0, -1), c(0, 1), c(1, -1), c(1, 0), c(1, 1), c(0,0))
  
  # Helper function to safely add edges
  add_edge  =  function(i, j) {
    if (i >= 1 && i <= n*n && j >= 1 && j <= n*n) {
      adj_matrix[i,j]  =  1
      adj_matrix[j,i]  =  1
    }
    return(adj_matrix)
  }
  
  # Map each square to its neighbors
  for (row in 1:n) {
    for (col in 1:n) {
      index  =  (row - 1) * n + col
      
      for (move in 1:nrow(moves)) {
        neighbor_row  =  row + moves[move, 1]
        neighbor_col  =  col + moves[move, 2]
        if (neighbor_row > 0 && neighbor_row <= n && neighbor_col > 0 && neighbor_col <= n) {
          neighbor_index  =  (neighbor_row - 1) * n + neighbor_col
          if(adj_matrix[index,neighbor_index] == 0){
            adj_matrix = add_edge(index, neighbor_index) 
          }
        }
      }
    }
  }
  if(timer_ == T){
    end  =  Sys.time()
    time_taken  =  end - start
    return(list(matrix = adj_matrix, time = time_taken))
  } else {
    return(adj_matrix)
  }
}

if(file.exists(here("intermediate_products",paste0("adjacency_", size, ".mtx")))){
  adjacency_ = readMM(here("intermediate_products",paste0("adjacency_", size, ".mtx")))
}else{
  adjacency_ = kings_graph(size)[1][[1]]
  writeMM(adjacency_, file = here("intermediate_products",paste0("adjacency_", size, ".mtx")))
}

# Set biodiv
max_biodiv = as.numeric(Matrix(1, nrow = 1, ncol = size^2, sparse = T)%*%
  adjacency_ %*%
  Matrix(1, ncol = 1, nrow = size^2, sparse = T))

### Static optimization ####

fitness_function <- function(treatments,
                             B_ = budget) {
  # Inputs : 
    # Treatment is a binary vector of size N^2
    # Landscape is a vector as well 
  
  # Apply treatments to the landscape
  treated_landscape = landscape * (1 - treatments) 
  
  # Compute the first quadratic form
  score1 = as.numeric(t(Matrix(ifelse(treated_landscape == 2, 1, 0),
                    sparse = T)) %*% 
    adjacency_ %*% 
    Matrix(ifelse(treated_landscape == 2, 1, 0), sparse = T))
  
  score2 = as.numeric(t(Matrix(ifelse(treated_landscape > 0, 1, 0), 
                    sparse = T)) %*% 
    adjacency_ %*% 
    Matrix(ifelse(treated_landscape > 0, 1, 0), sparse = T))
  
  # Define adaptive constraints : 
  constraint_budget = B_ - sum(treatments)
  constraint_biod   = const_ - score2
  
  penalty1 = ifelse(constraint_budget >=0, 0, 10^4*abs(constraint_budget))
  penalty2 = ifelse(constraint_biod <= 0, 0, 10^4*abs(constraint_biod))
  
  # Compute the objective function
  result = -(score1 + penalty1 + penalty2)
  return(result)
}

repair_function = function(pop) {
  max_ones = budget
  for (i in 1:nrow(pop)) {
    num_ones = sum(pop[i,])
    if (num_ones > max_ones) {
      ones_indices = which(pop[i,] == 1)
      excess_ones = sample(ones_indices, num_ones - max_ones)
      pop[i, excess_ones] = 0
    }
  }
  return(pop)
}

scores = function(landscape, type = 'B'){
  score1 = as.numeric(t(Matrix(ifelse(landscape == 2, 1, 0),
                    sparse = T)) %*% 
    adjacency_ %*% 
    Matrix(ifelse(landscape == 2, 1, 0), sparse = T))
  
  score2 = as.numeric(t(Matrix(ifelse(landscape > 0, 1, 0), 
                    sparse = T)) %*% 
    adjacency_ %*% 
    Matrix(ifelse(landscape > 0, 1, 0), sparse = T))
  if(type == 'B'){
    return(score2)
  }else{
    return(score1)
  }
}

```

Do a diagnosis of the landscape : what is the original risk, what is the original biodiversity score? Indeed, if the biodiversity score already does not meet the biodiversity constraint, we do not act. 

```{r, original diagnosis}
dat_og = data.frame(
  biod_og = scores(landscape),
  fuel_og = scores(landscape, 'F')
)
head(dat_og)
```

To improve on the genetic algorithm, a selection of initial solution may be better. My initial results show that:
* When the biodiversity constraint is low, need to tackle the most central nodes.
* When the biodiversity constraint is average, the budget is still respected, but treatments are reshuffled at lower degree nodes
* When the biodiversity constraint is large, the budget is not respected, less are treated, and treatments are reshuffled to lower degree nodes

```{r, function for selection}
degrees = as.vector(t(Matrix(ifelse(landscape == 2, 1, 0),
                    sparse = T)) %*% 
    adjacency_)

generate_binary_matrix <- function(N, length_of_vector, preferential_locations, X) {
  # N: number of binary vectors to generate
  # length_of_vector: the length of each binary vector
  # preferential_locations: indices where the 1s are preferentially located
  # X: maximum number of 1s in each vector

  # Initialize a matrix to store the generated binary vectors
  binary_matrix <- matrix(0, nrow = N, ncol = length_of_vector)
  
  for (i in 1:N) {
    # Initialize a binary vector with all 0s
    binary_vector <- rep(0, length_of_vector)
    
    # Randomly select the number of 1s to place, not exceeding X
    num_ones = X
    
    # Ensure preferential locations are not greater than the number of available positions
    num_preferential <- min(num_ones, length(preferential_locations))
    
    # Randomly select indices from preferential locations for the 1s
    if (num_preferential > 0) {
      selected_indices <- sample(preferential_locations, num_preferential)
    } else {
      selected_indices <- integer(0)
    }
    
    # Place 1s in the selected preferential locations
    binary_vector[selected_indices] <- 1
    
    # If needed, fill the remaining 1s in non-preferential locations
    remaining_ones <- num_ones - num_preferential
    if (remaining_ones > 0) {
      # Define non-preferential locations
      non_preferential_locations <- setdiff(1:length_of_vector, preferential_locations)
      
      # Randomly select remaining positions for the 1s
      remaining_indices <- sample(non_preferential_locations, remaining_ones)
      
      # Place the remaining 1s
      binary_vector[remaining_indices] <- 1
    }
    
    # Store the generated binary vector in the matrix
    binary_matrix[i, ] <- binary_vector
  }
  
  return(Matrix(binary_matrix, sparse = T))
}

```



Then, I run the genetic algorithm : 

```{r, genetic}
popSize_ = 200


const_ = round(max_biodiv/5)


if(const_ <= dat_og$biod_og){
  if(const_ <= .3*max_biodiv){
    suggestions_ = generate_binary_matrix(popSize_, 
                                      size^2,
                                      which(degrees== max(degrees)),
                                      budget)
  }else{
    suggestions_ = generate_binary_vectors(popSize_, 
                                          size^2,
                                          which(degrees != max(degrees)), budget)
    # random_:
    suggestions_random = matrix(rbinom(popSize_ * size^2, 1, budget/size^2*0.9), nrow = popSize_, ncol = size^2)
  }
  
  if(size %in%c(3,4)){
    maxIter_ = 25
  }else{
    maxIter_ = 100
  }
  
  timer__ = Sys.time()
  
  ga_result = ga(
    type = "binary",
    fitness = fitness_function,
    nBits = size^2,       # Number of bits in the binary vector (size of the landscape)
    maxiter = maxIter_,   # Number of generations
    popSize = popSize_,    # Population size
    pcrossover = 0.8,# Crossover probability
    pmutation = 0.2, # Mutation probability
    suggestions = suggestions_,
    monitor = T
  )
  print(Sys.time() - timer__)
### Illustration to see if it works
  summary(ga_result)
  
}else{
 print('Baseline landscape cannot accomodate biodiversity constraint')
}
```

I just give solutions with a good level of budget constraint satisfaction. It could be worth something to investigate a different initial solution based on my previous findings : 

1. Compute node distribution in the two graphs
2. Find the largest degree nodes in both graphs
3. Depending on the value of the constraint, play on the selection of potential treatments such that : 
* If low, just a solution that respects the budget
* If medium, keep budget but not at the largest degree nodes. 
* If high, lower budget and find some nodes with large degree and low degree. 

Something is weird here : there's something I don't get, with what constraint is fucked at some point; is it the biodiversity constraint, or the budget constraint. I think it may be the biodiversity constraint that is not satisfied with a given budget. Maybe there's a way for me to fix or redirect the search? Like tell the algorigthm, at some point, look in this direction. 
Illustrate the results : 

```{r, statistics of output}
# Find lowest budgets : 
budg_eff = vector('list', nrow(ga_result@solution))

for(i in 1:nrow(ga_result@solution)){
  budg_eff[i] = sum(ga_result@solution[i,])
}
budg_eff = unlist(budg_eff)
treatment_id = which(budg_eff == min(budg_eff))
if(length(treatment_id)>1){
 treatment_id = treatment_id[1,]
}


treatment_ = ga_result@solution[treatment_id,]
budg_effective = sum(treatment_)

fuel_score= as.numeric(t(landscape*(1-treatment_))>1)%*%adjacency_%*% as.numeric(landscape*(1-treatment_)>1)
biod_score= as.numeric(t(landscape*(1-treatment_))>0)%*%adjacency_%*% as.numeric(landscape*(1-treatment_)>0)

dat_ = data.frame(budget = budget, 
                  expenses = budg_effective, 
                  risk= as.numeric(fuel_score), 
                  risk_reduction = (dat_og$fuel_og - as.numeric(fuel_score))/dat_og$fuel_og*100,
                  constraint = const_, 
                  biodiv = as.numeric(biod_score))
head(dat_)
```
So everything seems to be satisfied here. Need to find a way to reshuffle the decision when the algo is stuck somewhere. 


```{r, plots of outputs}
a = rr
a = setValues(a, matrix(landscape, nrow = size))
#plot(a)

viz_landscape(a)



b = rr
b = setValues(b, matrix(landscape*(1 - treatment_), nrow = size))
#plot(b)

viz_landscape(b)

```
Plot of treatments and degrees : 

```{r, degrees and treatments}
c = rr
c = setValues(c, matrix(treatment_, nrow = size))
plot(c)
#viz_landscape(c)

d = rr
d = setValues(c,matrix(degrees, nrow=size))
plot(d)

```


Evaluate the solutions : 

```{r, evaluate solutions}
as.numeric(t(landscape*(1-treatment_))>1)%*%adjacency_%*% as.numeric(landscape*(1-treatment_)>1)


treatment_b = c(0,0,0,0,1,1,1,0,0,0,0,0,0,0,0,0)
as.numeric(t(landscape*(1-treatment_b))>1)%*%adjacency_%*% as.numeric(landscape*(1-treatment_b)>1)

```


```{r, other approach}

best_solution <- ga_result@solution

# Ensure the final population contains the best solutions found
final_population <- ga_result@population
best_individuals <- final_population[order(apply(final_population, 1, fitness_function), decreasing = TRUE), ]

b = rr
b = setValues(b, matrix(landscape*(1 - best_individuals[26,]), nrow = size))
plot(b)

```


## New Approach for 3 period dynamic optimization

The idea is clear : have a 3 period built in objective function, which takes as input a vector of , and returns the value, and the succession of optimal treatments

First, I import some basic functions :

* `kings_graph` : generates a king graph adjacency matrix for graph of with `size` nodes
* `mature_cells`: generates a binary vector for cells that can host biodiversity
* `burn_cells` : generates a binary vector for cells that can burn
* `mature_score`: generates the connectivity score associated with each objective
* `age_dyn`: computes the age dynamics
* `visualise_transition`: visualises the evolution of treatments and landscapes.

```{r, basic functions}
kings_graph  =  function(n, timer_ = T) {
  if(timer_ == T){
    start = Sys.time()
  }
  # Initialize the adjacency matrix with zeros
  adj_matrix  =  Matrix(0, nrow = n*n, ncol = n*n)
  # Define potential moves (king moves in chess)
  moves  =  rbind(c(-1, -1), c(-1, 0), c(-1, 1), c(0, -1), c(0, 1), c(1, -1), c(1, 0), c(1, 1), c(0,0))

  # Helper function to safely add edges
  add_edge  =  function(i, j) {
    if (i >= 1 && i <= n*n && j >= 1 && j <= n*n) {
      adj_matrix[i,j]  =  1
      adj_matrix[j,i]  =  1
    }
    return(adj_matrix)
  }
  
  # Map each square to its neighbors
  for (row in 1:n) {
    for (col in 1:n) {
      index  =  (row - 1) * n + col
      
      for (move in 1:nrow(moves)) {
        neighbor_row  =  row + moves[move, 1]
        neighbor_col  =  col + moves[move, 2]
        if (neighbor_row > 0 && neighbor_row <= n && neighbor_col > 0 && neighbor_col <= n) {
          neighbor_index  =  (neighbor_row - 1) * n + neighbor_col
          if(adj_matrix[index,neighbor_index] == 0){
            adj_matrix = add_edge(index, neighbor_index) 
          }
        }
      }
    }
  }
  if(timer_ == T){
    end  =  Sys.time()
    time_taken  =  end - start
    return(list(matrix = adj_matrix, time = time_taken))
  } else {
    return(adj_matrix)
  }
}

adjacency_ = kings_graph(size)$matrix

mature_cells = function(matrix){
  to_ret = Matrix(as.numeric(matrix>0), ncol = 1, sparse = T)
  return(to_ret)
}

burn_cells = function(matrix){
  to_ret = Matrix(as.numeric(matrix>1), ncol = 1, sparse = T)
  return(to_ret)
}

mature_score = function(matrix, 
                        type_ = 'B',
                        adj_ = adjacency_){
  if(type_ == 'B'){
    return(t(mature_cells(matrix)) %*% adj_ %*% mature_cells(matrix))
  }else{
    return(t(burn_cells(matrix)) %*% adj_ %*% burn_cells(matrix))
  }
}

age_dyn = function(landscape){
  landscape = Matrix(landscape, ncol = 1, sparse = T)
  #treatment = Matrix(treatment, ncol = 1, sparse = T)
  
  #augmented_mat = landscape + 1
  #capped_mat = pmin(augmented_mat, 2)
  
  #treatment_ = 1 - treatment
  #next_ = landscape * treatment_
  
  next_ = landscape + 1
  next_ = pmin(next_, 2)
  
  next_ = Matrix(as.numeric(next_), nrow = 1, byrow= T, sparse = T)
  return(next_)
}

visualise_transition = function(landscape, treatment){
  # Evaluate 3 landscapes : 
  landscape_init = as.vector(landscape)
  landscape_post_treat = unname(landscape*(1 - treatment[1: index1]))
  landscape_init1 = as.vector(age_dyn(landscape_post_treat))
  landscape_post_treat1 = as.vector(landscape_init1*(1 - treatment[index2:index3]))
  landscape_init2 = as.vector(age_dyn(landscape_post_treat1))
  landscape_post_treat2 = as.vector(landscape_init2*(1 - treatment[index4:index5]))
  
  markers_1 = c(rep('initial', size^2),
               rep('post_treat0', size^2),
               rep('initial1', size^2),
               rep('post_treat1', size^2),
               rep('initial2', size^2),
               rep('post_treat2', size^2))
  markers_2 = c(rep(0,2*size^2),
                rep(1,2*size^2),
                rep(2,2*size^2))
  
  dat_ =  as.data.frame(as.table(matrix(landscape_init,size,size)))%>%
      mutate(Var1 = as.numeric(Var1),
             Var2 = as.numeric(Var2))

  for(x in c('landscape_post_treat', 'landscape_init1', 'landscape_post_treat1', 
             'landscape_init2', 'landscape_post_treat2')){
    
    candit = eval(parse(text = x))
    dat__ = as.data.frame(as.table(matrix(candit, size, size)))%>%
      mutate(Var1 = as.numeric(Var1),
             Var2 = as.numeric(Var2))
    dat_ = rbind(dat_, dat__)
  }
  
  dat_ = dat_%>%
    mutate(markers1 = factor(markers_,
                            levels = c('initial', 'post_treat0', 'initial1',
                                       'post_treat1', 'initial2', 'post_treat2')),
           markers2 = factor(markers_2),
           Freq = as.factor(Freq))
  
  dat_ %>%
    ggplot(aes(x=Var1, y=Var2, fill = Freq))+
    geom_tile()+
    scale_fill_manual(values = green_palette)+
    facet_grid(markers2~markers1)+
    coord_fixed()
}

```


```{r, built in dynopt}

const_ = max_biodiv/5
index1= size^2
index2 = size^2+1
index3 = 2*size^2
index4 = 2*size^2+1
index5 = 3*size^2

jvlivs = function(treatments_, 
                  landscape_ = landscape,
                  B_ = budget,
                  constant_ = const_){
  # First try is landscape is 3*N^2
  # Generate indexes:

  
  # Generate treatments
  treatment1 = treatments_[1:index1]
  treatment2 = treatments_[index2:index3]
  treatment3 = treatments_[index4:index5]

  #Landscape and scores : 
  
    # Period 1 : 
  landscape_treated1 = landscape*(1 - treatment1)
  score_fuel1 = mature_score(landscape_treated1, "F")
  score_biod1 = mature_score(landscape_treated1)
  
  # Period 2:
  suppressWarnings({
      landscape_treated2 = age_dyn(landscape_treated1)*(1 - treatment2)
  })
  score_fuel2 = mature_score(landscape_treated2, "F")
  score_biod2 = mature_score(landscape_treated2)

  # Period 3:
  suppressWarnings({
      landscape_treated3 = age_dyn(landscape_treated2)*(1 - treatment3)
  })
  score_fuel3 = mature_score(landscape_treated3, "F")
  score_biod3 = mature_score(landscape_treated3)
  
  
  # Constraints : 
    # Period1
  constraint_budget1 = B_ - sum(treatment1)
  constraint_biod1   = constant_ - score_biod1
  
  penalty1_1 = ifelse(constraint_budget1 >=0, 0, 10^4*abs(constraint_budget1))
  penalty2_1 = ifelse(constraint_biod1 <= 0, 0, 10^4*abs(constraint_biod1))
    # Period2
  constraint_budget2 = B_ - sum(treatment2)
  constraint_biod2   = constant_ - score_biod2
  
  penalty1_2 = ifelse(constraint_budget2 >=0, 0, 10^4*abs(constraint_budget2))
  penalty2_2 = ifelse(constraint_biod2 <= 0, 0, 10^4*abs(constraint_biod2))
    # Period3
  constraint_budget3 = B_ - sum(treatment3)
  constraint_biod3   = constant_ - score_biod3
  
  penalty1_3 = ifelse(constraint_budget3 >=0, 0, 10^4*abs(constraint_budget3))
  penalty2_3 = ifelse(constraint_biod3 <= 0, 0, 10^4*abs(constraint_biod3))
  
  value_ = -(score_fuel1 + score_fuel2 + score_fuel3 +
    penalty1_1 + penalty1_2 + penalty1_3 +
    penalty2_1 + penalty2_2 + penalty2_3)
  
  return(as.numeric(value_))
}

tester = round(runif(3*size^2,0,1))
landscape
jvlivs(tester)
```


Evaluate the performance of the function : 

```{r, threepeat}
popSize_ = 200


const_ = round(max_biodiv/5)


#if(const_ <= dat_og$biod_og){
#  if(const_ <= .3*max_biodiv){
#    suggestions_ = generate_binary_matrix(popSize_, 
#                                      size^2,
#                                      which(degrees== max(degrees)),
#                                      budget)
#  }else{
#    suggestions_ = generate_binary_vectors(popSize_, 
#                                          size^2,
#                                          which(degrees != max(degrees)), budget)
    # random_:
suggestions_ = matrix(rbinom(popSize_ * 3*size^2, 1, budget/size^2*0.9), nrow = popSize_, ncol = 3*size^2)
#  }
  
#if(size %in%c(3,4)){
#  maxIter_ = 25
#}else{
#  maxIter_ = 100
#}

maxIter_ = 100

timer__ = Sys.time()
  
ga_result = ga(
    type = "binary",
    fitness = jvlivs,
    nBits = 3*size^2,       # Number of bits in the binary vector (size of the landscape)
    maxiter = maxIter_,   # Number of generations
    popSize = popSize_,    # Population size
    pcrossover = 0.8,# Crossover probability
    pmutation = 0.2, # Mutation probability
    suggestions = suggestions_,
    monitor = T
  )

print(Sys.time() - timer__)
### Illustration to see if it works
summary(ga_result)
  
#}else{
# print('Baseline landscape cannot accomodate biodiversity constraint')
#}

```

```{r, data on performance}
# Find lowest budgets : 
budg_eff = vector('list', nrow(ga_result@solution))

for(i in 1:nrow(ga_result@solution)){
  budg_eff[i] = sum(ga_result@solution[i,])
}
budg_eff = unlist(budg_eff)
treatment_id = which(budg_eff == min(budg_eff))
if(length(treatment_id)>1){
 treatment_id = treatment_id[1]
}
treatment_ = ga_result@solution[treatment_id,]


# Budgets
budg_effective0 = sum(treatment_[1:index1])
budg_effective1 = sum(treatment_[index2:index3])
budg_effective2 = sum(treatment_[index4:index5])

# Successions
post_treat0 = as.numeric(landscape * (1 - treatment[1:index1]))
post_treat1 = as.numeric(age_dyn(post_treat0) * (1- treatment[index2:index3]))
post_treat2 = as.numeric(age_dyn(post_treat1) * (1- treatment[index4:index5]))

# Scores 
fuel_score0 = scores(post_treat0,"F")
fuel_score1 = scores(post_treat1,"F")
fuel_score2 = scores(post_treat2,"F")

biod_score0 = scores(post_treat0,"B")
biod_score1 = scores(post_treat1,"B")
biod_score2 = scores(post_treat2,"B")

dat_ = data.frame(budget = budget, 
                  expenses0 = budg_effective0, 
                  expenses1 = budg_effective1, 
                  expenses2 = budg_effective2, 
                  #
                  risk0 = fuel_score0,
                  risk1 = fuel_score1,
                  risk2 = fuel_score2,
                  #
                  constraint = const_, 
                  biodiv0 = biod_score0,
                  biodiv1 = biod_score1,
                  biodiv2 = biod_score2)
head(dat_)


```

Now, function to visualize : 

```{r, vizualize succession}
visualise_transition(landscape,treatment_)
```




## NSGA II algorithm
```{r, new algo}
if(!("mco" %in% installed.packages())){
  install.packages("mco")
}
library(mco)
```

Use NSGA II algorithm, with two different objectives

```{r, adapted objective}

fitness_nsga = function(treatments){
  
}

```